---
title: "Modeling"
author: "aaron till"
date: "5/29/2018"
output: html_document
---
```{r}
library(caret)
library(glmnet)

```

```{r}
modeling_data <- dplyr::select(main_data_census, -FType, - FCode, - GNIS_Nm, - ReachCd, - Prmnn_I, - Year, - GNIS_ID, - site_id, - WBIC, - Winterkill, - Infection, - Anthropogenic, - MME, - Month, - Season, - Spring, - layer_dif, - quadratic_temp, - peak_temp, - long_round, - lat_round, - Ice_Duration) 
 
```
 
 
 
# Ridge regression 

```{r}

x_ridge <- model.matrix(Summerkill ~ ., modeling_data) 


y_ridge <- ifelse(modeling_data$Summerkill == 1, 1, 0)

```

```{r}

lambdatest <- glmnet(x_ridge, y_ridge, family = "binomial", alpha = 0)
plot(lambdatest, xvar = 'lambda')

```

```{r observing lambdas}
set.seed(1234)


# experimenting for quicker run, lambda = c(10^-5, 10^-3.5, 10^-4)

ridge_regression_lambda_summer <- cv.glmnet(x_ridge, y_ridge, family = "binomial", alpha = 0, nfolds = 3) # alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 

plot(ridge_regression_lambda_summer)

```

```{r making final lasso regression model}

ridge_regression_model_summer <- glmnet(x_ridge, y_ridge, family = "binomial", alpha = 0, lambda = ridge_regression_lambda_summer$lambda.1se) 
# alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 
#use $lambda.1se instead of $lambda.min for simpler but less accurate model

coef(ridge_regression_model_summer)

```

# Lasso regression 


```{r}

x_all <- model.matrix(Summerkill ~ . , modeling_data)

y_all <- ifelse(modeling_data$Summerkill == 1, 1, 0)


```

```{r}

lambdatest <- glmnet(x_all, y_all, family = "binomial", alpha = 1)
plot(lambdatest, xvar = 'lambda')
 
```

```{r observing lambdas}
set.seed(1234)

grid=10^seq(10,-15,length=100) # set lambda equal to for checking if more extensive lambda needed, no difference

# for quicker, lambda = c(10^-7, 10^-5.5, 10^-4)

lasso_regression_coords_lambda_summer <- cv.glmnet(x_all, y_all, family = "binomial", alpha = 1, nfolds = 3) # alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 

plot(lasso_regression_coords_lambda_summer)

```

```{r making final lasso regression model}

lasso_regression_coords_model_summer <- glmnet(x_all, y_all, family = "binomial", alpha = 1, lambda = lasso_regression_coords_lambda_summer$lambda.1se) 
# alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 
#use $lambda.1se instead of $lambda.min for simpler but less accurate model

coef(lasso_regression_coords_model_summer)

```


 
# Normal Logistic Regression modeling 


```{r creating reg_predictions and quartiles}
set.seed(1234)

regression_model <- glm(Summerkill ~ Mean_Surf_Temp + Mean_Surf_Zscore +layer_dif + Schmidt + population + V1 + V2, family = 'binomial', data=main_data_census) 

coef(regression_model)
```



# Building datasets for shrinkage model outputs


#Building ridge  predictions dataset 


```{r}
ridge_summer_predictions <- dplyr::select(future_data_census, -FType, - FCode, - GNIS_Nm, - ReachCd, - Prmnn_I, - GNIS_ID,- Month, - Season, - Spring, - layer_dif, - quadratic_temp, - peak_temp, - long_round, - lat_round, - year, - Ice_Duration)


ridge_summer_predictions$Summerkill <- 0 # Not sure why I am forced to make this


newx<- model.matrix(Summerkill ~ . - Year - WBIC - site_id, ridge_summer_predictions) #why NEWX has to be a fake model and not just a dataset is unclear)


ridge_summer_predictions$Prob <- as.vector(predict(ridge_regression_model_summer, newx= newx, type = 'response'))


ridge_summer_predictions$quantile <- quantile(ridge_summer_predictions$Prob,probs = c(.01, 25, 75)/100, na.rm = TRUE)


```


```{r forecasting}
set.seed(1234)

a <- ridge_summer_predictions$Prob
simulation_log_regress <- rbinom(length(a), 1, prob = a)

ridge_summer_predictions$Summerkill_forecast <- simulation_log_regress


```


#Building lasso predictions set

```{r}

lasso_coords_summer_predictions <- dplyr::select(future_data_census, -FType, - FCode, - GNIS_Nm, - ReachCd, - Prmnn_I, - GNIS_ID, - Month, - Season, - Spring, - layer_dif, - quadratic_temp, - peak_temp, - long_round, - lat_round, - year, - Ice_Duration)

lasso_coords_summer_predictions$Summerkill <- 0 # Not sure why I am forced to make this

newx<- model.matrix(Summerkill ~ . - Year - WBIC - site_id, lasso_coords_summer_predictions) #why NEWX has to be a fake model and not just a dataset is unclear)



lasso_coords_summer_predictions$Prob <- as.vector(predict(lasso_regression_coords_model_summer, newx= newx, type = 'response'))


lasso_coords_summer_predictions$quantile <- quantile(lasso_coords_summer_predictions$Prob,probs = c(.01, 25, 75)/100, na.rm = TRUE)

```

```{r forecasting}
set.seed(1234)

a <- lasso_coords_summer_predictions$Prob
simulation_log_regress <- rbinom(length(a), 1, prob = a)

lasso_coords_summer_predictions$Summerkill_forecast <- simulation_log_regress

```

# Building Normal Regression Dataset


```{r}

reg_predictions <- future_data_census
reg_predictions$Prob <- predict(regression_model,future_data_census, type = 'response')
reg_predictions$quantile <- quantile(reg_predictions$Prob,probs = c(min(reg_predictions$Prob), max(reg_predictions$Prob)), na.rm = TRUE)



```

```{r forecasting}
set.seed(1234)

a <- reg_predictions$Prob
simulation_log_regress <- rbinom(length(a), 1, prob = a)

reg_predictions$Summerkill_forecast <- simulation_log_regress

```



# Testing Models

```{r creating 50% random split for training/testing}

set.seed(1234)

train_indices <- sample(1:nrow(modeling_data), size = 528339 , replace = FALSE) # 4/5ths = 528339 #half = 330212
train_data <- slice(modeling_data, train_indices) 
test_data  <- slice(modeling_data, -train_indices)


train_data_reg <- slice(main_data_census, train_indices) 
test_data_reg  <- slice(main_data_census, -train_indices)

#flds <- createFolds(main_data_census, k = 5, list = TRUE, returnTrain = TRUE)

```









# Ridge Regression summerkill testing - test/training


```{r}

x_train <- model.matrix(Summerkill ~ ., train_data) 


y_train <- ifelse(train_data$Summerkill == 1, 1, 0)

```

making training model

```{r}
ridge_regression_train <- glmnet(x_train, y_train, family = "binomial", alpha = 0, lambda = ridge_regression_lambda_summer$lambda.1se) # alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 
#use lambda.1se instead of lambda.min for simpler but less accurate model
#can use lambda from regular model

#coef(lasso_regression_model)

``` 

testing for missclassification

```{r}

ridge_regression_test <- model.matrix(Summerkill ~ ., test_data)



probabilities <- ridge_regression_train %>% predict(newx = ridge_regression_test)
predicted_classes <- ifelse(probabilities > 0.5, 1, 0)
# Model accuracy 
observed_classes <- test_data$Summerkill
mean(predicted_classes == observed_classes)


```

testing for average probability seperation

```{r}

ridge_model_test <- test_data


ridge_model_test$Prob <- as.vector(predict(ridge_regression_train, newx= ridge_regression_test, type = 'response'))


ggplot(ridge_model_test, aes(x = factor(Summerkill), y = log(Prob))) +
  geom_boxplot()

ridge_model_test %>% group_by(Summerkill) %>% summarise(mean(Prob))

```

Testing for likelihood of fit


```{r}

ridge_model_test %>%
  summarise(likelihood = prod(ifelse(Summerkill == 1, Prob, (1-Prob))))


```


# Lasso COORDS + pop summerkill testing - test/training

Using training data from ridge regression

making training model

```{r}
lasso_coords_regression_train <- glmnet(x_train, y_train, family = "binomial", alpha = 1, lambda = lasso_regression_coords_lambda_summer$lambda.1se) # alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 
#use lambda.1se instead of lambda.min for simpler but less accurate model
#can use lambda from regular model

#coef(lasso_regression_model)

``` 

testing for missclassification

```{r}



lasso_coords_regression_test <- model.matrix(Summerkill ~ . ,test_data)



probabilities <- lasso_coords_regression_train %>% predict(newx = lasso_coords_regression_test)
predicted_classes <- ifelse(probabilities > 0.5, 1, 0)
# Model accuracy 
observed_classes <- test_data$Summerkill
mean(predicted_classes == observed_classes)


```

testing for average probability seperation

```{r}

lasso_coords_model_test <- test_data


lasso_coords_model_test$Prob <- as.vector(predict(lasso_coords_regression_train, newx= lasso_coords_regression_test, type = 'response'))


ggplot(lasso_coords_model_test, aes(x = factor(Summerkill), y = log(Prob))) +
  geom_boxplot()

lasso_coords_model_test %>% group_by(Summerkill) %>% summarise(mean(Prob))

```

Testing for likelihood of fit

```{r}

lasso_coords_model_test%>%
  summarise(likelihood = prod(ifelse(Summerkill == 1, Prob, (1-Prob))))


```

# regular regression testing


making training model

```{r}
reg_train <- glm(Summerkill ~  Mean_Surf_Temp + Mean_Surf_Zscore + layer_dif + Schmidt + population + V1 + V2 , family = 'binomial', data=train_data_reg) 
``` 

testing for missclassification

```{r}



probabilities <- predict(reg_train, test_data_reg, type = 'response')
predicted_classes <- ifelse(probabilities > 0.5, 1, 0)
observed_classes <- test_data$Summerkill
mean(predicted_classes == observed_classes)


```

testing for average probability seperation

```{r}

reg_predictions_test <- test_data_reg

reg_predictions_test$Prob <- predict(reg_train, test_data_reg, type = 'response')




ggplot(reg_predictions_test, aes(x = factor(Summerkill), y = log(Prob))) +
  geom_boxplot()

reg_predictions_test %>% group_by(Summerkill) %>% summarise(mean(Prob))

```

Testing for likelihood of fit

```{r}

reg_predictions_test %>%
    summarise(likelihood = prod(ifelse(Summerkill == 1, Prob, (1-Prob))))

  

```



#Supplementary all MME predictions (with lasso)


#Modeling


```{r}

mme_modeling_data <- dplyr::select(main_data_census, -FType, - FCode, - GNIS_Nm, - ReachCd, - Prmnn_I, - Year, - GNIS_ID, - site_id, - WBIC, - Winterkill, - Infection, - Anthropogenic, - Summerkill, - Month, - Season, - Spring, - layer_dif, - quadratic_temp, - peak_temp, - long_round, - lat_round, - Ice_Duration) 
 

```

```{r}

x_mme <- model.matrix(MME ~ . , mme_modeling_data)

y_mme <- ifelse(mme_modeling_data$MME == 1, 1, 0)


```

```{r}

lambdatest <- glmnet(x_mme, y_mme, family = "binomial", alpha = 1)
plot(lambdatest, xvar = 'lambda')
 
```

```{r observing lambdas}
set.seed(1234)


lasso_mme_lambda_summer <- cv.glmnet(x_mme, y_mme, family = "binomial", alpha = 1, nfolds = 3) # alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 

plot(lasso_mme_lambda_summer)

```

```{r making final lasso regression model}

lasso_mme_model_summer <- glmnet(x_mme, y_mme, family = "binomial", alpha = 1, lambda = lasso_mme_lambda_summer$lambda.min) 
# alpha = 0 ridge, 1 for lasso, between 0 and 1 for elastic 
#use $lambda.1se instead of $lambda.min for simpler but less accurate model

coef(lasso_mme_model_summer)

```



#Building


```{r}

lasso_MME_predictions <- dplyr::select(future_data_census, -FType, - FCode, - GNIS_Nm, - ReachCd, - Prmnn_I, - GNIS_ID, - Month, - Season, - Spring, - layer_dif, - quadratic_temp, - peak_temp, - long_round, - lat_round, - year, - Ice_Duration)

lasso_MME_predictions$MME <- 0 # Not sure why I am forced to make this

newx<- model.matrix(MME ~ . - Year - WBIC - site_id, lasso_MME_predictions) #why NEWX has to be a fake model and not just a dataset is unclear)



lasso_MME_predictions$Prob <- as.vector(predict(lasso_mme_model_summer, newx= newx, type = 'response'))

```




# User Model Data

```{r user data}
setwd('/home/aatill/Till_Thesis/Summer_Research_Work/MME_Climate_Change_Research/')

Lake_Names <-read.csv("Input_Data/Wi_Lakes_Maps .csv") 
```

```{r}
Lake_Risk_Assesment <- merge(select(lasso_coords_summer_predictions,WBIC, site_id, Year, Prob, Mean_Surf_Temp), select(Lake_Names, OFFICIAL_NAME, WBIC)) %>%
  filter(Year > 2020) %>%
  group_by(WBIC, site_id, Year, OFFICIAL_NAME) %>%
  summarise('Summerkill Probability' = sum(Prob), 'Mean Surface Temperature' = mean(Mean_Surf_Temp))

Lake_Risk_Assesment <- distinct(Lake_Risk_Assesment)

write.csv(Lake_Risk_Assesment, "Lake_Risk_Assessment.csv")

```
