---
title: "Supplementary Information"
author: "aaron till"
date: "6/18/2018"
output: html_document
---

```{r Infectious Agent Yearly Test}

combined_data_restricted$sig_all <- ifelse(combined_data_restricted$Cause.Category.4 == 'WINTERKILL', 'p<.05', 'p>.05')
combined_data_restricted$sig_all <- factor(combined_data_restricted$sig_all, levels = c('p>.05', 'p<.05'))

ultimate_zscore_boxplot <- mean_surf(combined_data_restricted) %>%
  filter(Cause.Category.4 == 'INFECTIOUS AGENT' | Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'ANTHROPOGENIC CONDITION' ) %>%
ggplot(aes(y = zscore_temp,x = Cause.Category.4)) +
  theme_tufte() +
  ylab('Zscore All Seasons')+
  xlab('Category of Killtype')+
  xlab(NULL) +
  geom_hline(yintercept = 0, alpha = 0.5) + 
  geom_boxplot(aes(fill = sig_all)) + 
  scale_fill_manual(values = c('grey', 'gold'), guide = guide_legend(title = 'T-test'))

ultimate_zscore_boxplot


ttest_data_all_anthro <- filter(mean_surf(combined_data_restricted), Cause.Category.4 == 'ANTHROPOGENIC CONDITION')
t.test(ttest_data_all_anthro$zscore_temp, mu = 0)

ttest_data_infectious_all<- filter(mean_surf(combined_data_restricted), Cause.Category.4 == 'INFECTIOUS AGENT')
t.test(ttest_data_infectious_all$zscore_temp, mu = 0)

ttest_data_all <- filter(mean_surf(combined_data_restricted), Cause.Category.4 == 'WINTERKILL')
t.test(ttest_data_all$zscore_temp, mu = 0)


```


```{r ice duration winterkill}

combined_data_restricted <- combined_data_restricted %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(is.na(Cause.Category.4)), 'SUMMER NO-EVENT'))

combined_data_restricted_winter <- combined_data_restricted %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(Cause.Category.4 == 'SUMMER NO-EVENT'), 'WINTER NO-EVENT')) 

combined_data_restricted_winter$sig_ice <- ifelse(combined_data_restricted_winter$Cause.Category.4 == 'WINTERKILL', 'p<.05', 'p>.05')
combined_data_restricted_winter$sig_ice <- factor(combined_data_restricted_winter$sig_ice, levels = c('p>.05', 'p<.05'))

ice_duration_boxplot <- mean_surf(combined_data_restricted_winter) %>%
  filter(Month == 'Jan' | Month == 'Feb' | Month == 'Dec' | Month == 'Mar') %>%
  filter(Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'WINTER NO-EVENT' ) %>%
ggplot(aes(y = ice_duration_days,x = Cause.Category.4)) +
  theme_tufte() +
  ylab('Ice Duration (Days)')+
  xlab('Category of Killtype')+
  xlab(NULL) +
  geom_hline(yintercept = 0, alpha = 0.5) + 
  geom_boxplot(aes(fill = sig_ice)) + 
  scale_fill_manual(values = c('grey', 'gold'), guide = guide_legend(title = 'ANOVA'))

ice_duration_boxplot

ice_anova_data <- mean_surf(combined_data_restricted_winter) %>%
  filter(Month == 'Jan' | Month == 'Feb' | Month == 'Dec' | Month == 'Mar') %>%
  filter(Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'WINTER NO-EVENT')

anova_ice <- aov(ice_duration_days ~ Cause.Category.4, ice_anova_data)
summary(anova_ice)
tuk <- TukeyHSD(anova_ice)
tuk
```

```
FIX THIS ^ and add test stats for above 2
```{r MME distribution}

main_data$Month = factor(main_data$Month, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", 'Oct', "Nov", "Dec"))  

plot1<-ggplot(filter(main_data, MME ==1),aes(x=factor(Year), fill=Month)) +
  stat_count()+
  #geom_boxplot(color="black",aes(y=peak_temp, group=Year)) +
  ylab("")+
  xlab("Year") +
  ggtitle("Number Of Events Per Year")+              #Peak Temperatures Per Year")+
  scale_x_discrete()+
  #guides(fill=FALSE) +
  theme_tufte()
  #scale_fill_brewer(palette = 'matlab.like', direction = -1)
plot1

#number of events per month

plot1.1<-ggplot(filter(main_data, MME == 1),aes(x=Month, fill=Month)) +
  stat_count()+
  xlab("Month")+
  ylab("")+
  ggtitle("Number Of Events Per Month")+
  scale_x_discrete() +
  guides(fill=FALSE) +
  theme_tufte()
  #scale_fill_brewer()
plot1.1

grid.arrange(plot1, plot1.1)




```

```{r}

main_data %>%
  filter(MME == 1) %>%
  group_by(WBIC) %>%
  summarise(n = n()) %>%
ggplot(aes(x = n)) +
  geom_bar() +
  ylab('Number of Lakes')+
  xlab('Number of Events') +
  theme_tufte()


```