---
title: "Visualization"
author: "aaron till"
date: "5/29/2018"
output: html_document
---

```{r}
library(ggplot2)
library(ggthemes)
library(ggmap)
library(car)
#library(gridExtra)
#library(Scales)
```

6 figures allowed

Captions < 300 words


# Starting spatial distribution

```{r}

Wisconsin_map <- get_map('Stevens Point, Wisconsin', zoom = 7, maptype = 'toner-lite', source = 'stamen')

```

```{r}




MME_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data, MME == 1), aes(x = V1, V2))


MME_lakes_of_wisconsin_dif_categories <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data, MME == 1 & Summerkill == 1), aes(x = V1, V2), fill = 'red', shape = 21) +
  geom_point(data = filter(main_data, MME == 1 & Winterkill == 1), aes(x = V1, V2), fill = 'blue', shape = 21) +
  geom_point(data = filter(main_data, MME == 1 & Infection == 1), aes(x = V1, V2), fill = 'green', shape = 21) +
   geom_point(data = filter(main_data, MME == 1 & Anthropogenic == 1), aes(x = V1, V2), fill = 'orange', shape = 21)


color_seperated_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data, MME == 0), aes(x = V1, V2), fill = 'blue', shape = 21)+
  geom_point(data = filter(main_data, MME == 1), aes(x = V1, V2), fill = 'red', shape = 21)
  
color_seperated_lakes_of_wisconsin

```


# bBoxplot of killtype mean temps

```{r}

mean_surf(combined_data_restricted) %>%
  filter(Month == 'Jul' | Month == 'Jun' | Month == 'Aug' | Month == 'May' | Month == 'Sep') %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(is.na(Cause.Category.4)), 'SUMMERTIME NON-EVENT')) %>%
  filter(Cause.Category.4 == 'INFECTIOUS AGENT' | Cause.Category.4 == 'SUMMERKILL' | Cause.Category.4 == 'SUMMERTIME NON-EVENT' | Cause.Category.4 == 'ANTHROPOGENIC CONDITION') %>%   
ggplot(aes(y = temperature,x = Cause.Category.4)) +
  theme_tufte() +
  ylab('Mean Surface Temperature May - September')+
  xlab('Category of Killtype')+
  geom_boxplot()



```



# AV plot for Summerkills 

Taken from feature selection of lasso regression of summerkill in modeling.Rmd


```{r sample}

set.seed(1234)

summer_sample_main_data <- merge(filter(main_data, Summerkill == 1), sample_n(filter(main_data, Summerkill == 0), size = 500), all = TRUE)

logreg_summerkill <- glm(Summerkill ~ Mean_Surf_Temp + Cumulative_Above_0 + V2, family = 'binomial', data= summer_sample_main_data)
summary(logreg_summerkill)

```

```{r}



log_plot_summerkill <- avPlot(logreg_summerkill, variable = 'Mean_Surf_Temp',xlab = 'Residuals of Mean Surface Temperature', ylab = 'Residuals of Summerkill')


log_plot_summerkill      

```




# AV plot for Winterkill

Taken from lasso feature selection of winterkill only in modeling.Rmd

```{r sample}

set.seed(1234)

winter_sample_main_data <- merge(filter(main_data, Winterkill == 1), sample_n(filter(main_data, Winterkill == 0), size = 500), all = TRUE)

logreg_winterkill <- glm(Winterkill ~ Mean_Surf_Temp + Cumulative_Above_0 + V2, family = 'binomial', data= winter_sample_main_data)
summary(logreg_winterkill)

```

```{r}



log_plot_winterkill <- avPlot(logreg_winterkill, variable = 'Mean_Surf_Temp',xlab = 'Residuals of Mean Surface Temperature', ylab = 'Residuals of Summerkill')


log_plot_winterkill      

```




# Final projected MME by year & season (include original MME data for concurrent)}






# final spatial probability dist.

```{r}


reg_predictions_spatial <- merge(shape_full, reg_predictions, all = FALSE)

logreg_at_risk_lakes_of_wisconsin <- ggmap(Wisconsin_map) + 
  geom_point(data = reg_predictions_spatial, aes(x = V1, V2, color = quantile))+
  scale_colour_brewer(type = "div")


```

