---
title: "Visualization"
author: "aaron till"
date: "5/29/2018"
output: html_document
---

```{r}

library(ggthemes)
library(ggmap)


```

6 figures allowed

Captions < 300 words



# Fig:1 Boxplot of killtype mean temps

```{r}

mean_surf(combined_data_restricted) %>%
  filter(Month == 'Jul' | Month == 'Jun' | Month == 'Aug' | Month == 'May' | Month == 'Sep') %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(is.na(Cause.Category.4)), 'SUMMERTIME NON-EVENT')) %>%
  filter(Cause.Category.4 == 'INFECTIOUS AGENT' | Cause.Category.4 == 'SUMMERKILL' | Cause.Category.4 == 'SUMMERTIME NON-EVENT' | Cause.Category.4 == 'ANTHROPOGENIC CONDITION') %>%   
ggplot(aes(y = temperature,x = Cause.Category.4)) +
  theme_tufte() +
  ylab('Mean Surface Temperature May - September')+
  xlab('Category of Killtype')+
  geom_boxplot()



```

# Starting spatial distribution

```{r}

Wisconsin_map <- get_map('Stevens Point, Wisconsin', zoom = 7, maptype = 'hybrid')

ggmap(Wisconsin_map)

```

```{r}




MME_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data_wisconsin, MME == 1), aes(x = V1, V2))

color_seperated_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data_wisconsin, MME == 0), aes(x = V1, V2), fill = 'blue', shape = 21)+
  geom_point(data = filter(main_data_wisconsin, MME == 1), aes(x = V1, V2), fill = 'red', shape = 21)
  
               

```



# AV plot for Summerkills}




```{r AV plot for Winterkill}


```



```{r Final projected MME by year & season (include original MME data for concurrent)}



```




```{r final spatial probability dist.}


shape_reg_predictions <- merge(shape_full, Reg_predictions, all = FALSE)

logreg_at_risk_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = shape_reg_predictions, aes(x = V1, V2, color = log(Prob)))


```

