---
title: "Visualization"
author: "aaron till"
date: "5/29/2018"
output: html_document
---

```{r}
library(ggplot2)
library(ggthemes)
library(ggmap)
library(car)
library(gridExtra)
library(scales)
library(car)
library(DescTools)

```

6 figures allowed

Captions < 300 words




# Boxplot of killtype mean temps

```{r}
combined_data_restricted <- combined_data_restricted %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(is.na(Cause.Category.4)), 'SUMMER NO-EVENT')) 

combined_data_restricted$sig <- ifelse(combined_data_restricted$Cause.Category.4 == 'SUMMERKILL', 'p<.05', 'p>.05')
combined_data_restricted$sig <- factor(combined_data_restricted$sig, levels = c('p>.05', 'p<.05'))

boxplot1 <- mean_surf(combined_data_restricted) %>%
  filter(Month == 'Jul' | Month == 'Jun' | Month == 'Aug' | Month == 'Sep') %>%
  filter(Cause.Category.4 == 'SUMMERKILL' | Cause.Category.4 == 'SUMMER NO-EVENT' | Cause.Category.4 == 'INFECTIOUS AGENT') %>%   
ggplot(aes(y = temperature,x = Cause.Category.4)) +
  theme_tufte() +  
  ylab(NULL)+
  xlab(NULL)+
  geom_boxplot(aes(fill = sig)) + 
  scale_fill_manual(values = c('grey', 'gold'), guide = guide_legend(title = 'ANOVA'))

boxplot2 <- mean_surf(combined_data_restricted) %>%
  filter(Month == 'Jul' | Month == 'Jun' | Month == 'Aug' | Month == 'Sep') %>%
  filter(Cause.Category.4 == 'SUMMERKILL' | Cause.Category.4 == 'INFECTIOUS AGENT' | Cause.Category.4 == 'SUMMER NO-EVENT') %>%   
ggplot(aes(y = zscore_temp,x = Cause.Category.4)) +
  theme_tufte() +
  ylab(NULL) +
  xlab('Category of Killtype')+
  geom_boxplot(aes(fill = sig)) +
  xlab(NULL) +
  geom_hline(yintercept = 0, alpha = 0.5)+ 
  scale_fill_manual(values = c('grey', 'gold'), guide = guide_legend(title = 'T-test'))

grid.arrange(boxplot1, boxplot2)


```

```{r Summer Anova}

anova_data <- mean_surf(combined_data_restricted) %>% filter(Month == 'Jul' | Month == 'Jun' | Month == 'Aug' | Month == 'Sep') %>% filter((Cause.Category.4 == 'INFECTIOUS AGENT' | Cause.Category.4 == 'SUMMERKILL' | Cause.Category.4 == 'SUMMER NO-EVENT'))



leveneTest(y = temperature ~ Cause.Category.4, data = anova_data, center = mean)
#cannot use ANOVA must use WELCH oneway.test

welch_cause_type <- oneway.test(temperature ~ Cause.Category.4, anova_data)
print(welch_cause_type)

DunnettTest(temperature ~ factor(Cause.Category.4), data = anova_data, control = 'SUMMER NO-EVENT')
```
```{r summer Zscore Anova}
#leveneTest(y = zscore_temp ~ Cause.Category.4, data = anova_data)

#anova_zscore_cause_Type <- aov(zscore_temp ~ Cause.Category.4,anova_data)
#summary(anova_zscore_cause_Type)
#tuk <- TukeyHSD(anova_zscore_cause_Type)
#tuk

ttest_data_summerkill <- filter(anova_data, Cause.Category.4 == 'SUMMERKILL')
t.test(ttest_data_summerkill$zscore_temp, mu = 0)


ttest_data_infectious_summer<- filter(anova_data, Cause.Category.4 == 'INFECTIOUS AGENT')
t.test(ttest_data_infectious_summer$zscore_temp, mu = 0)

ttest_data_infectious<- filter(mean_surf(anova_data), Cause.Category.4 == 'SUMMER NO-EVENT')
t.test(ttest_data_infectious$zscore_temp, mu = 0)

```

```{r winterkill boxplots}
combined_data_restricted <- combined_data_restricted %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(is.na(Cause.Category.4)), 'SUMMER NO-EVENT'))

combined_data_restricted_winter <- combined_data_restricted %>%
  mutate(Cause.Category.4 = replace(as.character(Cause.Category.4), which(Cause.Category.4 == 'SUMMER NO-EVENT'), 'WINTER NO-EVENT')) 

boxplot1_winter <- mean_surf(combined_data_restricted_winter) %>%
  filter(Month == 'Dec' | Month == 'Jan' | Month == 'Feb' | Month == 'Mar') %>%
  filter(Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'WINTER NO-EVENT') %>%   
ggplot(aes(y = temperature,x = Cause.Category.4)) +
  theme_tufte() +
  ylab('Mean Surface Temperature')+
  xlab(NULL)+
  geom_boxplot(aes(fill = sig))+ 
  guides(fill = FALSE)+ 
  scale_fill_manual(values = c('grey', 'gold'))

boxplot2_winter <- mean_surf(combined_data_restricted_winter) %>%
  filter(Month == 'Dec' | Month == 'Jan' | Month == 'Feb' | Month == 'Mar') %>%
  filter(Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'WINTER NO-EVENT') %>%   
ggplot(aes(y = zscore_temp,x = Cause.Category.4)) +
  theme_tufte() +
  xlab('Category of Killtype')+
  geom_boxplot(aes(fill = sig)) +
  xlab(NULL) +
  ylab('Zscore')+
  ylim(-2.5,2) +
  geom_hline(yintercept = 0, alpha = 0.5)+
  scale_fill_brewer()+ 
  guides(fill = FALSE)+ 
  scale_fill_manual(values = c('grey', 'gold'))

grid.arrange(boxplot1_winter, boxplot2_winter)

```

```{r winterkill Anova }

anova_data_winter <- mean_surf(combined_data_restricted_winter) %>%  
  filter(Month == 'Dec' | Month == 'Jan' | Month == 'Feb' | Month == 'Mar') %>%
  filter(Cause.Category.4 == 'WINTERKILL' | Cause.Category.4 == 'WINTER NO-EVENT')    

leveneTest(y =temperature ~ Cause.Category.4, data = anova_data_winter, center = mean)


anova_cause_Type <- aov(temperature ~ Cause.Category.4, anova_data_winter)
summary(anova_cause_Type)
tuk <- TukeyHSD(anova_cause_Type)
tuk
```

```{r winter Zscore Anova }


#leveneTest(y =zscore_temp ~ Cause.Category.4, data = anova_data_winter, center = mean)

#anova_zscore_cause_Type <- aov(zscore_temp ~ Cause.Category.4,anova_data_winter)
#summary(anova_zscore_cause_Type)
#tuk <- TukeyHSD(anova_zscore_cause_Type)
#tuk

ttest_data_winter<- filter(anova_data_winter, Cause.Category.4 == 'WINTERKILL')
t.test(ttest_data_winter$zscore_temp, mu = 0)

ttest_data_winter_all<- filter(mean_surf(anova_data_winter), Cause.Category.4 == 'WINTER NO-EVENT')
t.test(ttest_data_winter_all$zscore_temp, mu = 0)


```

```{r ultimate boxplots}


combined_data_restricted$Cause.Category.4 <- factor(combined_data_restricted$Cause.Category.4, levels = c('SUMMERKILL', 'NON-EVENT', 'INFECTIOUS AGENT', 'WINTERKILL', 'ANTHROPOGENIC CONDITION'))



xbox <- grid.arrange(boxplot1_winter, boxplot1,  ncol = 2, widths = c(3.4, 6))
ybox <- grid.arrange(boxplot2_winter,boxplot2, ncol = 2, widths = c(3.4, 6))

grid.arrange(xbox, ybox)

ttest_winter <- filter(combined_data_restricted, Cause.Category.4 == 'ANTHROPOGENIC CONDITION' )
t.test(ttest_winter$zscore_temp, mu = 0) # There are a lot of cold lakes without winterkills...

#scale of significance, anthropogenic and winterkill restricted both significant but much less so, problem with test

```









# Final projected MME by year & season (include original MME data for concurrent)}



```{r}


plot1<-main_data %>%
  group_by(Year) %>%
  filter(Year<2014) %>%
  summarise(Summerkill = sum(Summerkill), Temp = mean(Mean_Surf_Temp)) %>%
ggplot(aes(x=factor(Year), y = Summerkill, fill = Temp)) + 
  geom_bar(stat ='identity')+
  scale_fill_gradient(low = 'Blue', high = 'Red', limits = c(9, 16)) +
  #geom_boxplot(color="black",aes(y=peak_temp, group=Year)) +
  ylab("Actual MMEs")+
  xlab("2004-2013") +
  scale_x_discrete()+
  guides(fill=FALSE) +
  theme_tufte()+
  ylim(0,75) +
  theme(axis.text.x=element_text(angle=90,hjust=1), legend.position = 'left') 
plot1

plot2<-lasso_summer_predictions %>%
  filter(Year <2060 & Year > 2030) %>%  
  group_by(Year) %>%
  summarise(Summerkill = sum(Summerkill_forecast), Temp = mean(Mean_Surf_Temp) ) %>%
ggplot(aes(x=factor(Year),y = Summerkill, fill = Temp)) +
  geom_bar(stat ='identity')+
  scale_fill_gradient(low = 'Blue', high = 'Red', limits = c(9, 16)) +
  #geom_boxplot(color="black",aes(y=peak_temp, group=Year)) +
  ylab("Forecasted MMEs")+
  xlab("2041-2059") +
  scale_x_discrete()+
  guides(fill=FALSE) +
  theme_tufte()+
  ylim(0,75) +
  theme(axis.text.x=element_text(angle=90,hjust=1), legend.position = 'left') 
plot2



plot3<- lasso_summer_predictions %>%
  filter(Year >2060) %>%
  group_by(Year) %>%
  summarise(Summerkill = sum(Summerkill_forecast), Temp = mean(Mean_Surf_Temp) ) %>%
ggplot(aes(x=factor(Year),y = Summerkill, fill = Temp)) +
  geom_bar(stat ='identity')+
  scale_fill_gradient(low = 'Blue', high = 'Red', limits = c(9, 16)) +
  #geom_boxplot(color="black",aes(y=peak_temp, group=Year)) +
  ylab(label = NULL)+
  xlab("2081-2099") +
  scale_x_discrete()+
  #guides(fill=FALSE) +
  theme_tufte()+
  theme(axis.text.x=element_text(angle=90,hjust=1), legend.position = 'right') +
  ylim(0,75) 
plot3



 grid.arrange(plot1,plot2,plot3, ncol = 3, widths = c(0.6, 1, 1.2))

```

```{r qualitative analysis}

main_data %>%
  group_by(Year) %>%
  summarise(Summerkill = sum(Summerkill), Temp = mean(Mean_Surf_Temp)) %>%
  arrange(desc(Summerkill))

main_data %>%
  filter(Summerkill == 1) %>%
  summarise(mean = n()/10)


lasso_summer_predictions %>%
  filter(Year <2060 & Year > 2030) %>%
  group_by(Year) %>%
  summarise(Summerkill = sum(Summerkill_forecast), Temp = mean(Mean_Surf_Temp)) %>%
  arrange(desc(Summerkill))

lasso_summer_predictions %>%
  filter(Year <2060 & Year > 2030) %>%
  filter(Summerkill_forecast == 1) %>%
  summarise(mean = n()/19)


lasso_summer_predictions %>%
  filter(Year >2060) %>%
  group_by(Year) %>%
  summarise(Summerkill = sum(Summerkill_forecast), Temp = mean(Mean_Surf_Temp)) %>%
  arrange(desc(Summerkill))

lasso_summer_predictions %>%
  filter(Year >2060) %>%
  filter(Summerkill_forecast == 1) %>%
  summarise(mean = n()/19)

```


# spatial mappings

```{r}

bbox =c(-93, 42.4, -87, 46.9) 
Wisconsin_map <- get_map(bbox, zoom = 7, maptype = 'toner-background')
ggmap(Wisconsin_map, darken = c(0,'black')) 
 # geom_path(data = spatial_w, )

```


```{r concurrent maps}




MME_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data, MME == 1), aes(x = V1, V2))


MME_lakes_of_wisconsin_dif_categories <- ggmap(Wisconsin_map) +
  geom_point(data = filter(main_data, MME == 1 & Summerkill == 1), aes(x = V1, V2), fill = 'red', shape = 21) +
  geom_point(data = filter(main_data, MME == 1 & Winterkill == 1), aes(x = V1, V2), fill = 'blue', shape = 21) +
  geom_point(data = filter(main_data, MME == 1 & Infection == 1), aes(x = V1, V2), fill = 'green', shape = 21) +
   geom_point(data = filter(main_data, MME == 1 & Anthropogenic == 1), aes(x = V1, V2), fill = 'orange', shape = 21)

summarized_main_data<-main_data %>%
  group_by(WBIC) %>%
  summarise(MME = max(Summerkill), V1 = mean(V1), V2 = mean(V2))

color_seperated_lakes_of_wisconsin <- ggmap(Wisconsin_map) +
  geom_point(data = arrange(summarized_main_data, MME), aes(x = V1, V2, fill = MME, alpha = MME),shape = 21, size = 1)+
  scale_fill_gradient(low = 'Blue', high = 'Red', limits = c(0, 1)) +
  theme(axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        #axis.text.y=element_blank(), 
        #axis.ticks.y=element_blank()
        )+
    guides(fill=FALSE, alpha = FALSE) +
  ggtitle('2004-2013')
  #geom_point(data = filter(main_data, MME == 0), aes(x = V1, V2), fill = 'blue', shape = 21)+
  #geom_point(data = filter(main_data, MME == 1), aes(x = V1, V2), fill = 'red', shape = 21)
  
color_seperated_lakes_of_wisconsin

```


```{r future}


summarized_lasso_summer_predictions_p2 <- lasso_summer_predictions %>%
  filter(Year > 2030 & Year < 2070) %>%
  group_by(WBIC) %>%
  summarise(Prob = sum(Prob), V1 = mean(V1), V2 = mean(V2)) 

summarized_lasso_summer_predictions_p3 <- lasso_summer_predictions %>%
  filter(Year > 2070) %>%
  group_by(WBIC) %>%
  summarise(Prob = sum(Prob), V1 = mean(V1), V2 = mean(V2)) 

summarized_lasso_summer_predictions_both <- lasso_summer_predictions %>%
  filter(Year > 2020) %>%
  group_by(WBIC) %>%
  summarise(Prob = sum(Prob), V1 = mean(V1), V2 = mean(V2)) 

logreg_at_risk_lakes_of_wisconsin_period_2 <- ggmap(Wisconsin_map) + 
  geom_point(data = arrange(summarized_lasso_summer_predictions_p2, Prob), aes(x = V1, V2, fill = Prob, alpha = Prob),shape = 21, size = 1)+
  scale_fill_gradient(low = 'Blue', high = 'Red',na.value = 'red', limits = c(0, 1)) +
    theme(axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  guides(fill=FALSE, alpha = FALSE) +
  ggtitle('2041-2059 Projected')
logreg_at_risk_lakes_of_wisconsin_period_2 


logreg_at_risk_lakes_of_wisconsin_period_3 <- ggmap(Wisconsin_map) + 
  geom_point(data = arrange(summarized_lasso_summer_predictions_p3, Prob), aes(x = V1, V2, fill = Prob, alpha = Prob),shape = 21, size = 1)+
 scale_fill_gradient(low = 'Blue', high = 'Red', na.value = 'Red', limits = c(0, 1)) +
    theme(axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        legend.key.size = unit(0.3, 'cm'), 
        legend.text= element_text(size = 5),
        legend.title = element_text(size = 10))+
  guides(alpha = FALSE) +
  ggtitle('2081-2099 Projected')
logreg_at_risk_lakes_of_wisconsin_period_3 


```
```{r}


grid.arrange(color_seperated_lakes_of_wisconsin,logreg_at_risk_lakes_of_wisconsin_period_2, logreg_at_risk_lakes_of_wisconsin_period_3, ncol = 3, widths = c(1.1,1,1.3))


```



